\input preamble
% if you want to know what this is good for, look at kai.tex.  kai, oct'14

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}

% --------------------------------------------------------
\section*{Style Guide}
\label{sec:styleguide}

Please ...

\begin{itemize}

\item write in American English.

\item use the symbols and adhere to the conventions formulated in Chapter~\ref{ch:conventionsSymbols}.

\item reference chapters, sections, figures, tables etc. as "Section~\ref{sec:trafficflowmodel}" etc.

\item reference equations as "Equation~(\ref{eq:matsimUTF})"

\item do not use MATSim-$\{T\lvert F\}$ anymore. It is a framework not a toolkit. Just use "MATSim". \url{http://matsim.org/conceptual-meeting/2012/notes}

\item write units as full word, as long as they are not in an equation: "meters" instead of "m".

\item write 100\,000 (with a small "\textbackslash," space between the thousands)

\item use "$x$\,unit" (with a small "\textbackslash," space between the number and the unit) (unless unit is a single superscript character) space is also required for \% (DIN 5008))

\item do not use "(e.g, citet\{x,y,z\})" but rather "citep[e.g.,][]\{x,y,z\}"

\item write time data like 8\,am, or 1:30\,pm

\item Capitalize words in item lists, except when splitting a single sentence by ","

\end{itemize}

\vfill\eject

% --------------------------------------------------------
\section*{Todo}

\begin{itemize}

\item check for micro-simulation vs. mobsim (Mail Kai, 19.11.)

\item change "choice" to "innovation"

\item ref(Nagel) from tub.bib instead of ivt\_bibs.bib

\item chase "he-only" formulations

\item correct "gls(...)".

\item merge the bibliographies somehow.

\item define MATSim roles \emph{strictly}. ???? Chapter~\ref{ch:developmentprocess}
\begin{itemize}
\item User (no programming), 
\item API-user (programming against API, not part of code base) 
\item API-developer (programming against API, part of the code base, no core changes), 
\item Core developer (changes in the core)
\end{itemize}
\ah{Man könnte den Developer-Schnitt aber auch beim Programming anstatt bei der Codebase legen, dann gäbe es keinen API-user. Both approaches are non-beauties. grmml}

\item destination innovation

\item check multi-modal chapter

\item finish glossary

\item Chef corrs einbauen

\end{itemize}

\vfill\eject

% --------------------------------------------------------
\lstset{language=Java}
\pagenumbering{gobble}

% ===========================================================================
% book frontmatter

\phantomsection
%\addcontentsline{toc}{chapter}{Title Page}
\createtitlepage
\pagenumbering{roman}

\phantomsection
%\addcontentsline{toc}{chapter}{Impressum}
\input{frontmatter/impressum} \cleardoublepage

\phantomsection
%\addcontentsline{toc}{chapter}{Table of Contents}
{\parskip0pt %hack to get toc condensed; please replace by cleaner 
% syntax if you know it.  kai, oct'14
\tableofcontents \cleardoublepage
}

\input{frontmatter/contributors} \cleardoublepage

%\addcontentsline{toc}{chapter}{List of Figures}
%\listoffigures \cleardoublepage

%\addcontentsline{toc}{chapter}{List of Tables}
%\listoftables \cleardoublepage

\input{frontmatter/editorsforeword} \cleardoublepage

%\addcontentsline{toc}{chapter}{Preface}
\input{frontmatter/preface} \cleardoublepage

\addtocontents{toc}{\bigskip}

\pagenumbering{arabic}

% ===========================================================================
% book body

% -----------------------
\part{Using MATSim} \cleardoublepage
\input{using/introducing} \cleardoublepage
\input{using/lgstarted} \cleardoublepage
\input{using/scoring} \cleardoublepage
\input{using/scenarios} \cleardoublepage

% -----------------------
\part{Extending MATSim} \cleardoublepage
\input{extending/modules/modules} \cleardoublepage

\input{extending/modules/destinationchoice} \cleardoublepage

\input{extending/modules/withinday} \cleardoublepage

\input{extending/modules/pt} \cleardoublepage
\input{extending/modules/multimodalsim} \cleardoublepage
\input{extending/modules/freight}
\input{extending/modules/carsharing} \cleardoublepage
\input{extending/modules/jointtrips} \cleardoublepage
\input{extending/modules/taxis} \cleardoublepage
\input{extending/modules/parking} \cleardoublepage
\input{extending/modules/elvehicles} \cleardoublepage
\input{extending/modules/air} \cleardoublepage
\input{extending/modules/roadpricing} \cleardoublepage
\input{extending/modules/emissions} \cleardoublepage
\input{extending/modules/accessibility} \cleardoublepage
\input{extending/modules/evacuation} \cleardoublepage
\input{extending/modules/wagonSim} \cleardoublepage
\input{extending/modules/signalslanes} \cleardoublepage
\input{extending/modules/psim} \cleardoublepage

\input{extending/modules/via} \cleardoublepage
\input{extending/modules/otfvis} \cleardoublepage
\input{extending/modules/cadyts} \cleardoublepage
\input{extending/modules/matsim4urbansim} \cleardoublepage
\input{extending/modules/networkeditor} \cleardoublepage
\input{extending/modules/business_analytics} \cleardoublepage

\input{extending/modules/abandoned} \cleardoublepage

\input{extending/development_process} \cleardoublepage
\input{extending/yourownmodules} \cleardoublepage

% -----------------------
\part{Understanding MATSim} \cleardoublepage
\input{understanding/history} \cleardoublepage
%\input{understanding/basicprocedure} \cleardoublepage
\input{understanding/agentbasedassignment} \cleardoublepage
\input{understanding/montecarlo} \cleardoublepage
\input{understanding/discretechoice} \cleardoublepage
\input{understanding/kinematicwaves} \cleardoublepage
\input{understanding/eco} \cleardoublepage

\bookmarksetup{startatroot}
\input{researchavenues} \cleardoublepage

% ===========================================================================
% book backmatter
\addtocontents{toc}{\bigskip}

\printglossary[type=\acronymtype] \cleardoublepage
\printglossary \cleardoublepage

\phantomsection
\addcontentsline{toc}{chapter}{Symbols \& Typographic Conventions}
\input{backmatter/symbolsTypography}

\phantomsection
\addcontentsline{toc}{chapter}{\bibname}
\bibliography{0/added_bibs,0/ivt_bibs,0/tub,0/ref-gunnar,0/michalm_matsim_book} \cleardoublepage

\phantomsection
\addcontentsline{toc}{chapter}{Index}
\printindex \cleardoublepage

\end{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% Local Variables:
% mode: latex
% mode: reftex
% mode: visual-line
% comment-padding: 1
% fill-column: 9999
% End: 
