% !TeX root = ../../../main.tex
Paratransit is an informal, market-oriented, and self-organizing public transport system. Despite the great importance of this transport mode it is mainly unsubsidized and only relies on the collected fares. 
Paratransit systems can be categorized by route pattern and function, by
organization of drivers, kind of stops, and fare type. Most case studies covered by the thesis of \citet[][]{Neumann_PhDThesis_2014} indicate that
paratransit services are mainly organized as route associations operating 8-15
seater vans on fixed routes. Most of the services run in direct competition to a
public transport system of a public transit authority. Such a service---minibuses with fixed routes but without fixed schedule---is often called a jitney service.
The minibus module of MATSim is based on those most common characteristics with the understanding that the jitney/minibus
service is one out of many possible paratransit services..

The minibus model is integrated in the multi-modal multi-agent simulation of MATSim. In the model, competing minibus operators start exploring the public transport market offering their services. With more successful operators expanding and less successful operators going bankrupt, a sustainable network of minibus services evolves. In \citet[][]{Neumann_PhDThesis_2014}, the model is verified through multiple illustrative scenarios that analyze the model's sensitivity towards different demand patterns, transfers, and the interactions of minibuses and a formal operator's fixed train~line.

The minibus model can be applied to two different fields of transport planning. First, there is the simulation of real paratransit that aims to help understand the implications that lie within the relationship of the different paratransit stakeholders. The model is able to create ``close-to-reality'' minibus networks in a South African context. \citet[][]{NeumannEtAl2014MinibusRSA} give an in-depth presentation of the application of the module and paratransit in South Africa in general.

Second, the same model provides a demand-driven approach to solve the network design problem of a formal transit authority. Thus, it can be used as a planning tool for the optimization of single transit lines or networks. For more details on the second form of application see Section~\ref{sec:paratransit_application}.

For further reading: \citet[][]{Neumann_PhDThesis_2014} provides an understanding of the underlying principles of paratransit services, namely minibus services, its stakeholders, fares, route functions, and patterns. Furthermore, it contains an in-depth description of the minibus model, its theoretical background, and its application to illustrative scenarios as well as real world examples.




