\section*{Impressum}
\ah{Impressum to be added by the publisher}

% ##################################################################################################################
\section*{Photos}
\ah{Probably placed somewhere else}

- Book Cover: ... illustrating ... \copyright Dr.~Marcel Rieser, \gls{senozon}.
- Using MATSim chapter cover: Portland, Oregon. View from the south to the city center, out of the Portland Aerial Tram. June 2008. \copyright Dr. Marcel Rieser, \gls{senozon}\\
- Extending MATSim chapter cover: Zurich, Switzerland. Tracks at Zurich Main Station. May~2011. \copyright Dr.~Marcel Rieser, \gls{senozon}\\
- Understanding MATSim chapter cover. Berne, Switzerland. Car and bike park at Berne Main Station. June~2011. \copyright Dr.~Marcel Rieser, \gls{senozon}\\
- Scenarios chapter cover. Gotthard railway model at the Swiss Museum of Transport, Lucerne, Switzerland. February~2004. \copyright Dr.~Marcel Rieser, \gls{senozon}\\

% ##################################################################################################################
\section*{Cite the Book}
\begin{itemize}\styleItemize
\item \imp{MLA:} Horni, Andreas, Kai Nagel, and Kay W. Axhausen, eds. \emph{The Multi-Agent Transport Simulation MATSim}. Publisher,~2015.
%
\item \imp{APA:} Horni, A., Nagel, K., \& Axhausen, K.~W. (Eds.). (2015). \emph{The Multi-Agent Transport Simulation MATSim}. Publisher.
%
\item \imp{Chicago:} Horni, Andreas, Kai Nagel, and Kay W. Axhausen, eds. \emph{The Multi-Agent Transport Simulation MATSim}. Publisher,~2015.
%
\end{itemize}

% ##################################################################################################################
%\url{http://www.thebookdesigner.com/2009/09/parts-of-a-book/}:
%``Copyright page: Usually the verso of the title page, this page carries the copyright notice, edition information, publication information, printing history, cataloging data, legal notices, and the books ISBN or identification number. In addition, rows of numbers are sometimes printed at the bottom of the page to indicate the year and number of the printing. Credits for design, production, editing and illustration are also commonly listed on the copyright page.''
