\section*{Style Guide}
\label{sec:styleguide}

Please ...

\begin{itemize}\styleItemize

\item write in American English.

\item use the symbols and adhere to the conventions formulated in Chapter~\ref{ch:conventionsSymbols}.

\item reference chapters, sections, figures, tables etc. as "Section~\ref{sec:trafficflowmodel}", Figure~\ref{fig:matsimcycle} etc.

\item reference equations as ``Equation~(\ref{eq:matsimUTF})''

\item do not use MATSim-$\{T\lvert F\}$ anymore. It is a framework not a toolkit. Just use ``MATSim''. \url{http://matsim.org/conceptual-meeting/2012/notes}

\item write units as full word, as long as they are not in an equation: ``meters'' instead of ``m''. \ah{check this! with \url{http://people.physics.illinois.edu/Celia/Lectures/Numbers.pdf}}

\item Write numbers 1-9 as words, if they are counted (not measured nor calculated ... on the base of whatever is seen as the fundamental difference between counting an calculating by the rule makers.) \url{http://people.physics.illinois.edu/Celia/Lectures/Numbers.pdf}

\item write 100\,000 (with a small ``\textbackslash,'' space between the thousands)

\item use ``$x$\,unit'' (with a small ``\textbackslash,'' space between the number and the unit) (unless unit is a single superscript character) space is also required for \% (DIN 5008))

\item do not use ``(\eg citet\{x,y,z\})'' but rather ``citep[e.g.,][]\{x,y,z\}''

\item write time data like 8\,am, or 1:30\,pm

\item Capitalize words in item lists, except when splitting a single sentence by ``,''

\item no comma after cf. \url{http://blog.apastyle.org/apastyle/2010/05/its-all-latin-to-me.html}. Use macro \cf

\item normal (in-sentence) space after i.e.,\ and e.g.,\ \url{http://tex.stackexchange.com/questions/2229/is-a-period-after-an-abbreviation-the-same-as-an-end-of-sentence-period}. Use the macros \eg \ie 

\item use ``abc'' and not "abc"

\item make sure you distinguish  \gls{microsimulation} vs. \gls{mobsim} (Mail Kai, 19.11.)

\item make sure to include both males and females (he/she ...)

\item \gls{senozon} logo only required on detailed figures (acc to mr)

\item place footnotes after punctuation, see \eg \url{https://hamilton.edu/documents/Footnotes.pdf} 

\item put references for acronyms in acronyms.tex

\end{itemize}