%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% When to use "newacronym" and "newglossaryentry"? 
% When used (referenced) for the first time both entries and accronyms are replaced by the short description in the text (not the one in the []-brackets). 
% For all further referencing only the name is shown.
% Accronyms, additionally show the abbreviation in brackets for the first time.

%##############################################################################################################################

\newglossaryentry{activity}{
    name=Activity,
    description={...},
		text={activity}
}

\newglossaryentry{agent}{
    name=Agent,
    description={...},
		text={agent}
}

\newglossaryentry{contribution}{
    name=Contribution,
    description={Often also called "contrib".},
		text={contribution}	
}

\newglossaryentry{facility}{
    name=Facility,
    description={Facilities are optional elements in MATSim to further specify an activity location.},
		text={facility}
}

\newacronym[description={Handbook on Emission Factors for Road Transport, 
version 3.1, see \url{www.hbefa.net}}]{hbefa}{HBEFA}{Handbook on Emission 
Factors for Road Transport}

%\newglossaryentry{implementation}{
    %name=Implementation,
    %description={...},
		%text={implementation}
%}

\newglossaryentry{iterations}{
    name=Iterations,
    description={A MATSim run is composed of a configurable number of iterations in an equilibrium search process.},
		text={iterations}	
}

\newglossaryentry{java}{
    name=JAVA,
    description={Java is a object-oriented modern programming language with cross-platform abilities},
		text={JAVA programming language}
}

\newglossaryentry{leg}{
    name=Leg,
    description={A leg is part of a trip performed with a single mode. In transport planning this is often called a stage.},
		text={leg}
}

\newglossaryentry{link}{
    name=Link,
    description={MATSim networks are composed of nodes and links representing the streets.},
		text={link}
}

\newglossaryentry{matsimrun}{
    name=MATSim run,
    description={},
		text={MATSim run}	
}

\newglossaryentry{node}{
    name=Node,
    description={MATSim networks are composed of nodes and links representing the streets.},
		text={node}
}

%\newglossaryentry{objectivefunction}{
    %name=Objective function,
    %description={...},
		%text={objective function}
%}

\newglossaryentry{plan}{
    name=Plan,
    description={An agent's plan contains his or her day schedule and after run completion an associated score.},
		text={plan}	
}

\newglossaryentry{replanning}{
    name=Replanning,
    description={...},
		text={replanning}	
}

\newglossaryentry{scenario}{
    name=Scenario,
    description={...},
		text={scenario}
}

\newglossaryentry{score}{
    name=Score,
    description={...},
		text={score}
}

\newglossaryentry{study}{
    name=Study,
    description={...},
		text={study}
}

\newglossaryentry{stage}{
    name=Stage,
    description={A leg is part of a trip performed with a single mode. In MATSim called leg.},
		text={stage}
}

\newglossaryentry{transit}{
    name=Transit,
    description={...},
		text={transit}
}

\newglossaryentry{trip}{
    name=Trip,
    description={...},
		text={trip}
}

\newglossaryentry{utility}{
    name=Utility,
    description={...},
		text={utility}
}

% ========================================================================

%day plan = schedule
%
%contribution = MATSim extensions (do not use extension as a name anymore?)
%
%transit
% ##############################################################################################################################
