% ##################################################################################################################
\section{Brussels}
\label{ch:scenarios:brussels}
\hfill \textbf{Author:} Daniel Röder

The \acrshort{matsim}-scenario for Brussels was developed in the project 
\acrshort{sustaincity}. The overall goal of this project was to couple an 
urban landuse model, in this case \acrshort{urbansim}, with the mobility 
simulation \acrshort{matsim}. This was done to evaluate the impact of 
transport policies to urban landuse and vice versa. A detailed description of 
the coupling of both models is e.g. given by \citet{Nicolai2013PhD}. A 
detailed description of the development of the scenario is given by 
\citet{RoederNagel2013SketchPlanningBrussels}.

The scenario covers the greater Brussels area in Belgium. The input data for 
the scenario is derived from two main sources. The population is directly 
generated from the \acrshort{urbansim}-model which covers a total number of 
860,214 persons. Per person a home- and a work-location is given and 
converted into a daily home-work-home plan. For computational reasons a 
randomly drawn population sample of one percent is used. 
\citet{OpenStreetMap2014} is used for the generation of the street network 
which consists of 10,861 nodes and 19,830 links, i.e. mainly the trunk road 
network was used.

For the modeling of public transport two different approaches are tested. The 
first approach is the \acrshort{matsim} default approach for scenarios where 
no detailed transitschedule is available. It is based on either beeline 
distance and average speed or network-based freespeed travel times and a 
certain factor. The second approach was not part of the \acrshort{matsim}-
core during the project but available as a contribution called 
matrixBasedPtRouter. It is based on OD travel time matrices between 
transitstops, i.e. travel times for all relations are computed in a pre-
process. The travel times may be based on a real-world-schedule or certain 
assumptions which may take spatial coverage into account. The advantages of 
this model are obvious. On the one hand it may depict the spatial coverage 
with public transport supply and thus the distance to the next transit stop 
influences the travel time. On the other hand it may depict the real network, 
i.e. routes and lines and possible waiting times for switching. Both 
approaches were compared against travel times and mode share measures from a 
SATURN\footnote{\citep{SATURN_Webpage_2014}}-model. Since the matrix-based 
approach comes closer to this model further investigations are based on this 
approach.

To evaluate the sensitivity of the model to certain policies a cordon toll 
scenario was set up. The toll is charged between 6 and 10 am every time a car 
passes the border of the cordon, i.e. every time a car enters a link which 
crosses the border of the cordon which is defined by the brussels freeway ring. 
For both scenarios accessibility was calculated and compared against each other. 
A detailed analysis is given by \citet{RoederNagel2013SketchPlanningBrussels}.

% ##################################################################################################################
